Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-09-04 tex/reply-to-referees.tex

\item  We adjusted the timing of monthly dummies for estimating behavior equation ($PI \to B$)  in Table 3.  In the previous version, the definition of monthly dummies for behavior equation ($PI \to B$) is different from that for case growth equation ($BPI \to Y$)  or ($PI \to Y$). This issue is now fixed.
%\item We made some grammatical adjustments.
\end{enumerate}

%No other changes of substance are made.
}

\replytitle
\subsection*{Reply to Editor}
\refreplyheading

\changes

In addition to our reply to the referee report, we also attached our reply to the comments we have received from
C. Jessica E. Metcalf (\url{https://metcalflab.princeton.edu/people/metcalf-c-jessica/}) who gave us a set of detailed comments via private communication.

\subsection*{Reply to Editor's Comments}
\begin{itemize}

@@

The autocorrelation component is captured by the lags of this variable in the dynamic specification. In addition,
we cluster the standard errors by state (capturing the impact of temporal dependence in the series, 
not accounted for by the lag structure).

We believe that it is better to use the number of cases and deaths rather than time since start of the outbreak as a  general framework to analyze the spread of COVID-19. This is especially true if we analyze the second wave of COVID-19, where time since start of the first outbreak may not be so relevant, and identifying the start of the second outbreak may be difficult.

\item \textit{`` Figure 8 - I do like seeing the data, but it also just raises questions, as you say, confounders + many other things at play.... I wondered if there would be a way to create a visual that captured a bit more of this, and pinpointed the anomalies which are where the inferential power lies. ''}

This is an interesting suggestion. We thought about the possibility of providing a version of Figure 8 (now, Figure 10) based on the regression residuals after taking out the effect of confounders etc but, eventually, we decided not to present such results due to the space constraint.

For your reference, we have constructed a version of  figure based on the residuals of regressing the case or death growth rates on state characteristics, month dummies, and their interactions, which illustrates that states with a mask mandate tend to have lower case and death growths even after controlling for confounders.    % and then computing their average value for states with or without a mask mandate for each date.

### 2020-09-04 tex/covidEffectOfNPI-revision.tex
update

\begin{figure}[ht]
  \caption{Case and death growth conditional on mask mandates \label{fig:masks}}\vspace{0.2cm}
 \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-cases-14}
      &
        \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-deaths-21}
    \end{tabular}
    \begin{flushleft}
      \scriptsize In these figures, red points are the case or death
      growth rate in states without a mask mandate. Blue points are
      states with a mask mandate 14 (21 for deaths) days prior. The
      red line is the average across states without a mask mandate 14
      (21 for deaths) days earlier. The blue line is the average
      across states with a mask mandate 14 (21 for deaths) earlier.
    \end{flushleft}
  \end{minipage}
\end{figure}

@@

We now analyze how behavior and policies together influence case and death
growth rates. We begin with some simple graphical evidence of the
effect of policies on case and death growth. Figure \ref{fig:masks}
shows average case and death growth conditional on date and whether
masks are mandatory for employees.\footnote{We take 14 and 21 day lags of mask policies for case and death growths, respectively, to  identify the states with a mask mandate because policies affect cases and deaths with time lags. See our discussion in the Appendix \ref{sec:timing}.  } The left panel of the figure shows
that states with a mask mandate consistently have 0-0.2 lower case
growth than states without. The right panel  also illustrates that
states with a mask mandate tend to have lower average death growth than states without a mask mandate.

>>>>

\begin{figure}[ht]
  \caption{Case and death growth conditional on mask mandates \label{fig:masks}}\vspace{0.2cm}
 \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-cases-14}
      &
        \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-deaths-21}
    \end{tabular}
    \begin{flushleft}
      \scriptsize In these figures, red points are the case or death
      growth rate in states without a mask mandate. Blue points are
      states with a mask mandate 14 (21 for deaths) days prior. The
      red line is the average across states without a mask mandate 14
      (21 for deaths) days earlier. The blue line is the average
      across states with a mask mandate 14 (21 for deaths) earlier.
    \end{flushleft}
  \end{minipage}%\\ \medskip
% \begin{minipage}{\linewidth}
%    \centering
%    \begin{tabular}{cc}
%      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-cases-res-14}
%      &
%        \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-deaths-res-21}
%    \end{tabular}
%    \begin{flushleft}
%      \scriptsize In these figures, red points are the regression residuals of case or death
%      growth rate on confounders in states without a mask mandate. Blue points are
%      states with a mask mandate 14 (21 for deaths) days prior. The
%      red line is the average across states without a mask mandate 14
%      (21 for deaths) days earlier. The blue line is the average
%      across states with a mask mandate 14 (21 for deaths) earlier.
%    \end{flushleft}
%  \end{minipage}
\end{figure}

We now analyze how behavior and policies together influence case and death
growth rates. We begin with some simple graphical evidence of the
effect of policies on case and death growth. Fgure \ref{fig:masks}
shows average case and death growth conditional on date and whether
masks are mandatory for employees.\footnote{We take 14 and 21 day lags of mask policies for case and death growths, respectively, to  identify the states with a mask mandate because policies affect cases and deaths with time lags. See our discussion in the Appendix \ref{sec:timing}.} The   left panel of the figure shows that states with a mask mandate consistently have 0-0.2 lower case
growth than states without. The  right panel also illustrates that
states with a mask mandate tend to have lower average death growth than states without a mask mandate.

%The lower two panels of figure \ref{fig:masks} are similar to the upper two panels except that we use the residuals of  regressing case or death growth on state-level characteristics, month dummies, and their interactions in place of  case or death growth, indicating that states with a mask mandate tend to have lower case and death growths even after controlling for confounders.

@@
